\documentclass[tom-ari]{subfile}
\begin{document}
	
	\chapter[1C]{\cl1}
		
	\section{New Proposed Responses}
		
	\Huge{\color{red}ALPHA}
		
	New Response Structure
	
	\normalsize
	
	The following is a proposed change to how we respond to \cl1, leaving us more precise definitions to lead into CIRKLE/SQUARE relays.
	
	\begin{bidtable}{\orauction{1c,?}}
		\di1 & No change, still negative. \\
		\he1 & (UPH) Extra values w/o hearts \\
		\he1 & (PH) Undefined, maybe split up clubs/diamonds. \\
		\sp1 & 5+ Hearts unbal.  This is unlimited, unlike the other GF responses.  TaJ has the extra values step. \\
		1NT & 5+ Spades unbal, no extras.  \cl2 TaJ, \sp2 is natural clubs. \\
		\cl2 & Clubs or Diamonds.  \di2 asks suit with LH \& zoom into TaJ with \diamondsuit\\
		\di2 & 4 \heartsuit without 4 \spadesuit.\\
		\he2 & 4 \spadesuit without 4 \heartsuit. \\
		\sp2 & 44 Majors \\
		2NT & \shape{5332} \clubsuit, R for LMH doubleton.\\ 
		\cl3 & \shape{5332} \diamondsuit, R for LMH doubleton \\
		\di3 & \exactshape{3244}:  Memory aid, low suit is short. \\
		\he3 & \exactshape{2344} \\
		\sp3 & \exactshape{3334} \\
		3NT & \exactshape{3343} \\
	\end{bidtable}

	Over \he1 response, \sp1 relay/waiting with all bids 1NT an higher as per direct.  (This is why \sp1 is unlimited and has the extra values step.)
	
	Over \di2/\he2, relay for shape. Table below is for both. 
	
	\begin{bidtable}{\orauction{1c,2d,2h,?}}
		+1 & \shape{5332}, relay for LMH doubleton. \\
		+2 & \shape{4432} with clubs, relay LH for doubleton \\
		+3 & \shape{4432} with diamonds, relay LH for doubleton \\
		+4 & \shape{4441} (short OM) \\
		+5 & \shape{4333}		\\
	\end{bidtable}

	Over \sp2, relay for shape.
	
	\begin{bidtable}{\orauction{1c,2s,2n}}
		\cl3 & \exactshape{4432}\\
		\di3 & \exactshape{4423}\\
		\he3 & \exactshape{4441}\\
		\sp3 & \exactshape{4414}\\
	\end{bidtable}

	Tying this into CIRKLE:  Once the shape is known, +1 (not 3NT) is a puppet to the next step, steps 1-4 are CIRKLE in ABCD suit order of SQUARE.  +2 (not 3NT) is a puppet to the next step, to then place the contract.  Bids above are natural and (if game) NF but encouraging.  Responder may bid on if they wish.
	
	Example
	
	\orauction{1c,2d,2h,2n,3c,3d} 
	
	shows \exactshape{3424}. \he3 would force \sp3 for CIRKLE steps.  3NT is hearts, \cl4 is clubs, \di4 is spades, \he4 is diamonds.
	
	Instead of \he3, 3NT would be natural and NF.  \sp3 would puppet to 3NT to sign off (anywhere). \cl4 and above are natural and encouraging but NF if a game bid.  

	\section{Current Responses}
	
	\cl1 is our general forcing opening, showing roughly 17+ HCP balanced or 16+ unbalanced.  The new ACBL convention charts allow for as low as 14 HCP for a forcing bid so long as it meets the rule of 24.  (i.e., 10 cards in 2 suits).  I don't know how much we will take advantage of the new rule, but it is worth noting.
	
	Like all strong club systems, the strength of the system lies not within the \cl1 opening itself but rather allowing for all other openers to be limited.  While we have some special sequences which allow for \"{u}ber max in TaJ sequences, most of our simple 1 level openings are going to be lighter than most people open.  All of our invitational and competitive decisions revolve around that fact.  This can be a factor in deciding between \cl1 and 1M, for example.
	
	\rem{As I noted in the mad science section, I'm open to changing the response structure if we feel it will better support good relays.}
	
	\begin{bidtable}{\orauction{1c,?}}
		\di1 & Negative, typically 0--7 HCP.  Can include bad 8s. \\
		\he1 & 5+ \spadesuit, GF. Generally 8+ HCP, good 7 is okay.  A+K is usually upgraded. \\
		\sp1 & Clubs or balanced (or by UPH limited \shape{4441}).  Clubs unlimited, balanced about 8--12. \\
		1NT & 5+ \heartsuit, GF \\
		\cl2 & 5+ \diamondsuit, GF \\
		\di2 &  Semi-positive transfer.  6+ \heartsuit, roughly 3-6 HCP.  Not GF \\
		\he2 &  Semi-positive transfer, 6+ \spadesuit, roughly 3-6 HCP.  Not GF \\ 
		Note & \rem{While I like the semi-positives, I recognize that they are taking up valuable bidding space that can likely be better utilized.} \\
		\sp2 & Big balanced.  No 5 card suit, 13+ HCP or 5+ controls. \\
		2NT & \exactshape{1444} 13+ HCP (PH 8--10) \\
		\cl3 & \exactshape{4441} 13+ HCP (PH 8--10) \\
		\di3 & \exactshape{4414} 13+ HCP (PH 8--10) \\
		\he3 & \exactshape{4144} 13+ HCP (PH 8--10) \\
		\sp3 & \rem{**NEW**} AKQxxxx, any suit.  This is different from older versions which had the \exactshape{1444} repeated. \\
		3NT--\he4 & 8 card suit transfers, very weak.  QJxxxxxx is expected maximum. \\
		\sp4 \& up & Undefined \\
	\end{bidtable}

	\section[1C--1D]{\cl1--\di1}
	
	\di1 is the general negative bid.  With the exception of the semi-positive transfers, this is the only bid which does not set up a GF auction.
	
	\rem{Crack theory time:  one of the ideas I am considering is what would happen in a \di1 ``waiting'' style instead of a ``negative''.  If \di1 could include some minimum balanced GFs, it could make some auctions easier.}
	
	Meckwell style rebids except 2NT is 20--21.
	
	\begin{bidtable}{\orauction{1c,1d,?}}
		\he1 & 4+ \heartsuit, can have a longer minor, 1RF.  Unbalanced or semi-balanced. Systemic rebid with 4=4=(4-1)\\
		\sp1 &  4+ \spadesuit, can have a longer minor, 1RF.  Unbalanced or semi-balanced.\\
		1NT & 17--19 bal, can have 5CM or 6Cm.  \shape{5422} also possible.\\
		\cl{2}/\di2 & Nat NF.  Denies 4CM.  Typically 6+ cards and unbalanced.\\
		\he2 & Kokish Relay.  Forces \sp2, Either GF with hearts or GF Bal.\\
		\sp2/\cl3/\di3 & GF Nat, typically 1 suited.\\
		2NT & 20--21 bal\\
		\he3 \& up & Undefined, although game bids are simply to play.		\\
	\end{bidtable}

	\begin{bidtable}{\orauction{1c,1d,1h,?}}
		\sp1 & 4+ \spadesuit, any strength.  Typically fewer than 4 \heartsuit.  Most rebids are natural NF, minor suits can be canap\'e. 2NT is an artificial big canap\'e (6+ m) 1RF.  Jumps encouraging but NF with jump shifts being 5--5. \\
		1NT & 0--5, no 4CM.  Rebids as per over \sp1, except \sp2 is a natural reverse and 1RF.\\
		\cl2 & 0--2 \heartsuit, 5+ to 7.  \di2 is waiting and scrambling, \he2 is natural and NF. Other GF.  2NT is a non-canap\'e GF, 3m is canap\'e.\\
		\di2 & Exactly 3 \heartsuit, 5+ to 7. \he2 NF, \he3 Inv.  2NT GF asking for shortness NLMH. Other 1RF, usually canap\'e.\\
		\he2 & 4+ \heartsuit, minimum. New suits are game tries, 2NT asks shortness NLMH.\\
		2NT & Best raise, nearly GF.  5+ \heartsuit ~common, \cl3 asks for shortness NLMH.\\
		JS & 6+ nat, 5+--7\\
		DJS & Splinter with exactly 4\heartsuit		\\
	\end{bidtable}
			

	
	\begin{bidtable}{\orauction{1c,1d,1s,?}}
		 & As per over \he1, except \he2 shows 5+ \heartsuit, 5+--7.
	\end{bidtable}
	
	\begin{bidtable}{\orauction{1c,1d,1n,?}}
		& 17--19, systems on as per 1NT opening.
	\end{bidtable}

	\begin{bidtable}{\orauction{1c,1d,2m,?}}
		& Natural, NF, denies 4CM.  No special follow ups. Jump Shift is a splinter.
	\end{bidtable}

	\begin{bidtable}{\orauction{1c,1d,2h,2s,?}}
		& \he2 is Kokish, forces \sp2.  Either \heartsuit ~or bal, GF.  No agreements about bids other than \sp2 by responder. \\
		2NT & GF Balanced.  Systems on as per 2NT opener. \\
		\cl3 & \heartsuit ~\& minor, \di3 for LH. \\
		\di3 & One suited \heartsuit \\
		\he3 & \heartsuit ~\& \spadesuit \\
		Other & ? \\
	\end{bidtable}
	
	\begin{bidtable}{\orauction{1c,1d,2n,?}}
		& 20--21, as per 2NT opener
	\end{bidtable}

	\begin{bidtable}{\orauction{1c,1d,Other}}
		& Other jumps are natural GF.  No special agreements other than \ldots\sp2--2NT is a spade raise.
	\end{bidtable}

%%%%

	\section[1C--1H]{\cl1--\he1}
	
	5+ \spadesuit, GF.  \spadesuit ~will be the longest suit.
	
	\sp1 semi-agrees \spadesuit, promising 2+ or 3+ if minimum (up to 19).  Begins TaJ Relay.  By UPH, extra values step applies.
	
	All other non-jump bids are natural.  1NT strongly tends to be (16)17-19 bal or short \spadesuit.  Jump bids are not defined.
	
	No follow ups to non-relay auctions, everything is natural. \rem{Clearly a good area to work on better agreements}
	
	\section[1C--1S]{\cl1--\sp1}
	
	GF, bal (or \shape{4441}) 8--12 or 5+ \clubsuit.
	
	1NT is most common rebid, and is simply waiting.  Direct 2 level bids are natural and promise 6+ cards in the suit. \rem{Adding this from discussion at the table in HI.}  Jumps are not defined.
	
	Over non-1NT rebids, it is expected that Responder bids \cl3 with clubs unless supporting.
	
	\begin{bidtable}{\orauction{1c,1s,1n,?}}
		\cl2 & 5+ \clubsuit.  \di2 TaJ (UPH extra values step), other natural with no special follow ups. \rem{New suits 5 cards?} \\
		\di2 & 4 \heartsuit, bal. \\ 
		\he2 & 4 \spadesuit, denies 4 \heartsuit, bal. \\
		\sp2 & No 4CM, bal.  \\
		2NT & \exactshape{1444} (UPH only) 8--12 \\
		\cl3 & \exactshape{4441} (UPH only) 8--12\\
		\di3 & \exactshape{4414} (UPH only) 8--12\\
		\he3 & \exactshape{4144} (UPH only) 8--12	\\
	\end{bidtable}
	
	Over one of the balanced 4 card transfers (e.g., \cl1--\sp1--1NT--\di2), the general style is bids on the \level{2} are strong and asking for controls in descending order (4--3--2--1--0).  Specifically \sp2 after \di2 has an extra step of 2NT to show 4+ \spadesuit, the other bids all show 2--3.  Over that 2NT extra step, \cl3 asks controls as above.
	
	\di2--3M or \he2--\sp3 are choice of games.  3NT or 4M is to play. Other bids are natural. \rem{Likely 5 cards?}

%%%

	\section[1C--1NT]{\cl1--1NT}
	
	\orauction{1c,1n}
	
	GF 5+ \heartsuit.  \cl2 is TaJ (UPH extra values step), \he2 is clubs, other is natural.  As per the \he1 response.
	
	\section[1C--2C]{\cl1--\cl2}
	
	\orauction{1c,2c}
	
	GF 5+ \diamondsuit.  \di2 is TaJ (UPH extra values step), other is natural.  As per the \he1 response. 
	
	\section{Semi-Positive Transfers}
	
	\cl1--\di2 and \cl1--\he2 show 6+ cards in the next suit (transfer) with invitational strength, usually around 3--6.  On rare occasions it could even be a ``game force'' based on shape instead of HCP.  (Responder simply rebids game over Opener accepting the transfer.)
	
	2M is NF, typically a non-fitting minimum.  2NT is also NF, although rarely bid over 2M.  3M agrees M and is GF with slam aspirations. New suits a natural and 1RF.
	
	\section{Strong 4x1}
	
	2NT thru \he3 all show \shape{4441} hands with 13+ HCP (UPH only, PH 8--10) bidding your singleton. (2NT is short \spadesuit). Openers rebids are natural, setting trump.  No special follow ups.  (Cuebids, RKC, etc.)
	  
 	\section[1C--3S]{\cl1--\sp3}
 	
 	\cl1--\sp3 shows a long good suit, AKQxxxx (7th) or better.  Typically this is intended to help with slam auctions and opener will know what suit responder is showing.
 	
 	This is a new agreement, as such there are no follow ups at this time.
 	
 	\section{8 card transfers}
 	
 	3NT thru \he4 show very weak hands with very long suits (8+) transfer style.  QJxxxxxx and out is about the best hand.  It expected that opener will most often bid Responder's suit, but other bids are natural.
 	
\end{document}




