\documentclass[tom-ari]{subfile}
\begin{document}
	
	\chapter{To Do List}
	
	Items that we have identified in play that need to make it into the notes.
	\begin{itemize}
		\item To Do
	\end{itemize}

	\section{Mad Scientist Labs}
	
	This is a section for crazy ideas that Tom has.  While this may seem like a low priority item given we are starting the notes from scratch, some of these ideas may have broad implications for the system.  In other words, this is a time to possibly reconstruct the system from the ground up, possibly changing things as we go.
	
	A few examples:
	
	\begin{itemize}
		\item Hand Evaluation - possible reworking our opening bids and responses using something like ZZs or Zar.  This may lead to better asking/showing sequences after shape is known.
		\item Replacing Stayman.  Stayman is Wrong, but a common evil.  I've researched other options and modified some of these ideas into something I like.  Essentially, \cl2\rightarrow\di2.  You lose weak majors, you gain getting out in \di2 and (main benefit) avoid revealing much about the 1NT opener's hand.  One item I haven't fully considered is long minor + 4CM.  Low priority item.
		
		\rem{Note 17 Oct 2020} Robinson/Boyd actually play something very much what I outlined here.  I think they use other bids to show the 4M/long m.  I need to study further and/or reach out to them.
	\end{itemize}

	\section{5 Nov 2020}
	\begin{itemize}
		\item identifying VLMH relays vs LMH for better shapes
		\item CIRKLE ok, need better defs when applies, temp agreement below 4 of our trump suit
		\item modified SQUARE when asker has known shortness? \rem{Don't we have this? Inverted singletons and skip voids.}
		\item Other CIRKLE auctions, after 1d-1M-1x e.g.
	\end{itemize}

   \section{Miscellaneous Competitive Auctions}
       Resp X over spades. \auctionpart{1s,x,2s,x}
         
       \ari{With some partners, I have played that this double is takeout, and \he3 by doubler promises \he{5}s while 2NT is artificial showing \he{4}s.} 
         
       See discussion: 
         
       \url{http://bridgewinners.com/article/view/1s-x-2s-x-minors-or-can-it-have-hearts/}
         
       \rem{I don't think I've addressed this either in notes or in person.  I don't have strong feelings in this area, although I wouldn't assume 2NT was Leb (like the link did).  Good point of discussion for this week if we get a chance. 28 Nov 19}
       
       \rem{17 Oct 20 - Never got to talk about this, I would need to be far more comfortable with this to consider it.}
          
	
\end{document}




